Supermartingales and Termination Analysis of Statistical PCF

### 2020-09-15 probabilisticProgrammingMartingales.tex
Add diagram to illustrate \sim_c using TikZ
The diagram currently looks really messy, but it's substantially complete.
It now requires lualatex to compile, because of the graph layouts

\input{Style/comment}
\usepackage{calculation}
\usepackage{graphicx}

\usepackage[square]{natbib}
\setcitestyle{aysep={}}

@@

\begin{figure}
\includegraphics[height=0.9\textheight]{akr-diagram.pdf}
\caption{\label{fig:adk-diagram} Some examples of the old version of the $\sim_p$- and $\sim_c$-rules}
\end{figure}

@@

For any term $N$ which is not a value, there is a unique environment $E$ and redex $R$ such that $N = E[R]$. The position of the hole in $E$ is equal to $\cbv(N)$, so that $N|\cbv(N) = R$, as the cases in the definition of $\cbv$ match the cases in the definition of environments. If $R \not= \tsample$, let $R'$ be the result of reducing $R$ (which is equal in both versions of the semantics), then $E[R'] = N[R' / \cbv(N)]$ therefore $\red(N,s) = (E[R'],s)$ and $(N,s) \Rightarrow_{\cbv} (E[R'],s)$. The distribution of next terms, conditional on the previous term, in the case that that previous term reduces deterministically, is therefore equal for $\red$ and $\Rightarrow_{\cbv}$.

>>>>

\input{Style/comment}
\usepackage{calculation}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning, graphs, quotes, graphdrawing, shapes.geometric}
\usegdlibrary{layered, circular}
\usepackage[square]{natbib}
\setcitestyle{aysep={}}

@@

\begin{figure}
\include{sim-diagram}
\caption{\label{fig:adk-diagram} Some examples of the $\sim_p$- and $\sim_c$-rules}
\end{figure}

@@

For any term $N$ which is not a value, there is a unique environment $E$ and redex $R$ such that $N = E[R]$. The position of the hole in $E$ is equal to $\cbv(N)$, so that $N|\cbv(N) = R$, as the cases in the definition of $\cbv$ match the cases in the definition of environments. If $R \neq \tsample$, let $R'$ be the result of reducing $R$ (which is equal in both versions of the semantics), then $E[R'] = N[R' / \cbv(N)]$ therefore $\red(N,s) = (E[R'],s)$ and $(N,s) \Rightarrow_{\cbv} (E[R'],s)$. The distribution of next terms, conditional on the previous term, in the case that that previous term reduces deterministically, is therefore equal for $\red$ and $\Rightarrow_{\cbv}$.
